Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-11 ijar-npb-ms.tex
Completion of software appendix.

\section{Sets of System Reliability Functions}

@@

With the structure defined and the individual components numbered, it 
just remains to specify the types of each component.  This can be done
using the \texttt{setCompTypes} function.  This function takes the
system graph and a list of component type names and corresponding
component numbers.  Thus, completing the example for Figure
\ref{fig:bridge-layout}:

@@

*** to be completed

>>>>

\section{Sets of System Reliability Functions}
\label{sec:setsofrel}

@@

With the structure defined and the individual components numbered, it 
just remains to specify the types of each component.  This can be done
using the \texttt{setCompTypes} function.  This function takes the
system graph and a list of component type names (as the tag) and corresponding
component numbers (as the value).  Thus, completing the example for Figure
\ref{fig:bridge-layout}:

@@

Once the system has been correctly described using an undirected graph
as above, the methods presented in Sections \ref{sec:nonparamapproach}
-- \ref{sec:setsofrel} can be used via the function
\texttt{nonParBayesSystemInferencePriorSets}.

The function prototype is:

\noindent\texttt{nonParBayesSystemInferencePriorSets(at.times, survival.signature,}

\noindent\texttt{~~~~~~~~~~test.data, nLower=2, nUpper=2, yLower=0.5, yUpper=0.5)}

Aside from the system design, which can be passed to the function via
the \texttt{survival.signature} argument, the remaining elements which
must be specified are the:
\begin{enumerate}
  \item grid of times at which to evaluate the posterior, ${\cal T} = \{t_1, \ldots, \tmax\}$, via the \texttt{at.times} argument.
  \item component test data $\vec{t}^k = (t^k_1, \ldots, t^k_{n_k})$ for $k=1,\dots,K$, via the \texttt{test.data} argument.
  \item prior sets via the range of prior parameter sets $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$, via the \texttt{nLower}, \texttt{nUpper}, \texttt{yLower} and \texttt{yUpper} arguments.
\end{enumerate}

The grid of times, \texttt{at.times}, is specified as simply a vector 
of time points.

The \texttt{test.data} argument is a list of component type names (as
the tag) and corresponding lifetime data (as the value), for example 
a toy sized dataset for each component would be expressed as:

\noindent\texttt{test.data=list("T1"=c(0.19, 0.73, 1.87, 1.17),}

\noindent\texttt{~~~~~~~~~~~~~~~"T2"=c(0.22, 0.27, 0.63, 1.80, 1.25, 1.95),}

\noindent\texttt{~~~~~~~~~~~~~~~"T3"=c(1.33, 0.65, 1.59))}

Finally, there are multiple options for specifying the prior parameter
sets.  Each of the \texttt{nLower}, \texttt{nUpper}, \texttt{yLower}
and \texttt{yUpper} arguments can be specified as:
\begin{itemize}
  \item a single value for a homogeneous prior across time and components.  e.g.\ \texttt{nLower=2} $\implies \nktzl=2 \ \forall\,k, t$
  \item a vector of values of length $|{\cal T}|$ (\texttt{length(at.times)}), for a time inhomogeneous prior which is identical across component types.
  \item a data frame of size $1\times K$, where each column is named the same as in the \texttt{survival.signature} and \texttt{test.data} arguments, for a time homogeneous prior which varies across component types.
  \item a data frame of size $|{\cal T}|\times K$, where each column is named the same as in the \texttt{survival.signature} and \texttt{test.data} arguments, for a time inhomogeneous prior which varies across component types.
\end{itemize}

With these arguments supplied,  \texttt{nonParBayesSystemInferencePriorSets} will then compute
the posterior sets automatically in parallel across the cores of a
multicore CPU and return a list with two objects, named \texttt{lower} 
and \texttt{upper}, containing respectively the lower and upper bound 
for the system reliability function $\Rsys(t)$.
